\documentclass[10pt,twocolumn]{article}

\usepackage{times}
\usepackage{fullpage}

\usepackage{booktabs}  % for \midrule
%\usepackage{subfigure}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xspace}
%\usepackage{pslatex}
%\usepackage{pifont}
%\usepackage{multirow}
%\usepackage{array}
%\usepackage{booktabs}
%\usepackage{cite}
\usepackage{url}
%\usepackage{cancel}
\usepackage{color,colortbl}
%\usepackage{microtype}
%\usepackage{textcomp}% http://ctan.org/pkg/textcomp
\usepackage{tabularx}
\usepackage{framed}
\usepackage[]{algorithm2e}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\usepackage{algorithmic}

\usepackage{listings}
%\usepackage{scrextend}
%\usepackage{mathtools}
\usepackage{pbox}

\let\labelindent\relax
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{calc,positioning}
\usepackage{lipsum,adjustbox}

%\usepackage{tikz}
%\usepackage{decorations.pathmorphing}
%\usepackage{assymb}

\usepackage[labelfont=bf]{caption}

%\theoremstyle{plain}
\newtheorem{theorem}{\bf{Theorem}}%[section]
\newtheorem{lemma}[theorem]{\bf{Lemma}}
\newtheorem{corollary}[theorem]{\bf{Corollary}}
\newtheorem{proofl}[theorem]{\bf{Proof}}
\newtheorem{proposition}[theorem]{\bf{Proposition}}

%\theoremstyle{definition}
\newtheorem{definition}{\bf{Definition}}%[section]
\newtheorem{observation}{\bf{Observation}}%[section] 

%\theoremstyle{remark}
\newtheorem{example}{\bf{Example}}
\newtheorem{notation}{\bf{Notation}}
\newtheorem{fact}{\bf{Fact}}

\usepackage{listings}
%%\usepackage{listings-golang}
\usepackage{color}

%\usepackage{sectsty}
%\sectionfont{\fontsize{12}{15}\selectfont}


\newcommand\mypara[1]{\vspace{.3em}\noindent\textbf{#1}}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Useful reviewing/feedback annotations
\input{annotations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\title{In-network Contention Resolution for Disaggregated Memory}
%\author{WORDS '21 Submission \#3}
\author{Stewart Grant and Alex C. Snoeren\\ UC San Diego}
\date{}

\maketitle

\section*{Abstract}

Passive remote memory remains the holy grail of disaggregation.  Most
existing systems for disaggregated memory either use remote memory
simply as a backing store, or design special-purpose data structures
that require some amount of processing co-resident with the remote
memory to manage and apply updates.  The few proposals for truly
passive remote memory perform well only with read-mostly workloads,
rapidly deteriorating in the face of even low levels of write
contention.  We propose to leverage in-network devices (specifically,
a programmable top-of-rack switch) to serialize remote memory accesses
and resolve any write conflicts in flight.  Our prototype is able to
completely avoid write contention in the recently published Clover
disaggregated key/value store, delivering a performance boost of
almost 50\% on our testbed under a mixed read/write workload.

\input{intro}
\input{clover}
\input{design}
\input{eval}
%\input{body}
\input{discussion}

\section*{Acknowledgments}

This work is supported in part by the Advanced Research Projects
Agency-Energy (ARPA-E) and the National Science Foundation (NSF)
through grant CNS-1911104.  The authors thank Alex Forencich and Cindy
Moore for assistance with our testbed, and Yiying Zhang and the
anonymous reviewers for helpful suggestions and feedback.  Additional
thanks to Yizhou Shan for his aid in building our own instance of
Clover, and special thanks to Steve and Don Grant of Halftime Holdings
Ltd. for providing workstations, Internet and coffee.

\balance
\vspace{-0.3cm}
{\footnotesize \bibliographystyle{acm}
\bibliography{paper}}
\vspace{-0.5cm}

\end{document}
