\begin{abstract}

Effectively sharing passive remote memory remains an open problem.
While emerging standards like CXL promise cache-coherent memory
pooling, spec-compliant hardware is not yet commercially
available and its feasibility at scale remains unproven.
%Fundamentally, any
%design must choose a serialization point and then ensure in-order
%communication and operation from that point on.
%Most performant
Existing RDMA-based systems employ optimistic concurrency
approaches that defer serialization to the remote memory server and
rely upon heavyweight RDMA atomics to ensure consistency.
Unfortunately, atomic operations scale poorly causing these approaches
to degrade rapidly under contention.

We present \sword, an approach to leveraging the
\textit{de facto} serialization point in rack-scale disaggregated
systems---the top-of-rack switch---to transparently resolve data races
in flight.  In cases where \sword\ has sufficient resources to
interpose on all requests, it can remove heavyweight atomic operations and
replace them with simple verbs, avoiding the hardware
performance bottleneck.  More generally, however, it can
safely operate on only a subset of the requests, dynamically adjusting
contending requests to avoid expensive client-based resolution in
those cases.  Under a YCSB-A workload, our P4-based prototype
dramatically improves the performance of Clover, a state-of-the-art
disaggregated key-value store: throughput rises by nearly $35\times$
while bandwidth usage and tail latency drop by 16 and 300$\times$, respectively.
%Further, by removing RDMA atomics, we avoid
%hardware-imposed scalability limits.
%of $\approx$2.7 MOP/s per queue pair.
  
%% Disaggregating memory from compute incurs extreme latency
%% penalties. These penalties are multiplied when remote memory is shared
%% and contended for. State of the art approaches for mitigating the cost
%% of contention use mostly lock-less data structures for accessing and
%% modifying remote memory with common case O(1) operations.
%% Unfortunately in the face of even modestly contended resources
%% opportunistic algorithms incur extreme performance degradation due to
%% multiple round trip times, and expensive atomic memory operations such
%% as compare and swap.

%% We present \sword, an in-network serializer

%% In this work we make the observation that all memory operations in a
%% rack scale disaggregation system pass through a centralized switch
%% which must serialize all remote memory accesses on the wire. We use
%% this implicit serialization to arbitrate access to rack scale
%% memory. We use Clover (a state of the art disaggregated key value
%% store) to show that our approach removes all conflict, and can provide
%% serialization which allows for the removal of expensive atomic locking
%% operations.

\end{abstract}
